### 2019-04-18 README.Rmd
readme updates

This repository contains the data and code for our project investigating whether overt attention to reward-related distractors can be suppressed under feature search conditions in the same way as for physically salient distractors (see Gaspelin, Leonard, & Luck, 2017 - Attn Percept Psychophys).

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

Or you can install this compendium as an R package, vmacfeaturesearch, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("danielpearson90/vmacfeaturesearch")
```
### Licenses

>>>>

This repository contains the data and analysis code for our project investigating whether overt attention to reward-related distractors can be suppressed under feature search conditions.

This repository contains data files that have been derived from the raw eye-tracker data. The raw eye-gaze files are very large and so are not stored here. They can be found at: <https://osf.io/yrdzv/>.

@@

> Pearson, D., Watson, P., Cheng, P., Most, S. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (`r format(Sys.Date(), "%Y")`. Investigating attentional suppression of reward-related distractors. Retrieved from <https://osf.io/yrdzv>

@@

### Licenses
